Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-27 RSVOptimization.rnw

\author{
    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{a}}\\
    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{a}}\\
    \authorstyle{Daniel Weinberger, PhD\textsuperscript{a}}
}

@@

\newcommand\frontmatter{
    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
    \frontmattersection{Short title}{\headertitle}
    \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health. The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide. RSV chemoprophylaxys is expensive. In the US, the prophylaxys schedule recommendation is published by the AAP. The AAP recommens the same schedule for all states other than Florida.}
    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
    \clearpage
    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript. Daniel Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript. Virginia Pitzer reviewed and revised the manuscript. All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
    \clearpage
}

>>>>

\author{
    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{a}}\\
    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{a}}\\
    \authorstyle{Daniel M. Weinberger, PhD\textsuperscript{a}}
}

@@

\newcommand\frontmatter{
    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
    \frontmattersection{Short title}{\headertitle}
    \frontmattersection{Conflict of interest disclosures}{Virginia E. Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines. Daniel M. Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic. Ben Artin reports no relevant conflicts.}
    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health. The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide. RSV chemoprophylaxys is expensive. In the US, the prophylaxis schedule recommendation is published by the AAP. The AAP recommens the same schedule for all states other than Florida.}
    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
    \clearpage
    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript. Daniel M. Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript. Virginia E. Pitzer reviewed and revised the manuscript. All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
    \clearpage
}

### 2020-07-27 paper/aap-pediatrics-cover.tex

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. In this manuscript, we developed a general method of evaluating timing of RSV prophylaxis and applied it to RSV-associated hospitalization data in Connecticut to show that regionally-adjusted prophylaxis regimens would confer a modest improvement over the current AAP-recommended regimen.

>>>>

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. The American Academyc of Pediatrics makes recommendations about when to start prophylaxis against RSV. Aside from Florida, the recommended start date is the same for the entire US. Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation. We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen. This general approach could be used to evaluate the timing of prophylaxis in other states as well.

### 2020-07-27 paper/structure.tex
Separated supplemental figures

\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures
\usepackage{subcaption}

@@

\newcommand{\authorstyle}[1]{{\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)

>>>>

\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures
\usepackage{subcaption}
\DeclareCaptionType{supplementalfigure}[Supplemental Figure][List of supplemental figures]

@@

\newcommand{\authorstyle}[1]{{\noindent\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)
